\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}

\title{3 idiots movie review}
\author{Dheeraj}

\begin{document}

\maketitle

\section{Story}
 Rancho, Raju and Farhan enter the elite engineering college, only to learn lessons of life that cannot be taught through books and classrooms. Principal Viru Sahastrabuddhe is no help at all.

\section{Movie Review}
Rest assured, all ye desi cinema buffs, Aal Izz Well in apna Bollywood. If 2009 can begin with Dev D and end with 3 Idiots, it is indeed time to sound the seetis and taalis for one of the most exciting years of contemporary Indian cinema. Truly, this has been the year of the I.d.i.o.t in movielore: the Intrinsically intelligent, Downright smart, Inimitable, Original and Talented film maker, actor, story teller, musician, lyricist, dialogue writer and producer.\\

3 Idiots is the perfect end to an exciting year for India: the year when the aam aadmi voted in progress, liberalism, secularism and turned his back to corruption, communalism, regionalism. The three idiots, Rancchoddas Shyamaldas Chanchad (Aamir Khan), Raju Rastogi (Sharman Joshi) and Farhan Qureshi (R Madhavan), are perfect archetypes of the new age Indian who is essentially a non-conformist, questioning outmoded givens, choosing to live life on his own terms and chartering new roads that consciously skirt the rat race. Of course, they begin on the beaten track -- due to societal/parental pressure -- but refuse to become cogs in the wheel. Naturally, they end up as the Frostian hero (Robert Frost's Road Not Taken) who made all the difference to his life, and the world, by taking the road less travelled by.

\section{Performances}
Performances: Believe it or not, but Aamir, Madhavan and Sharman actually look -- and behave -- like students. While Aamir pitches in a near-perfect portrayal of Rancho, the free-spirited innovator, Madhavan and Sharman are perfectly in sync too. Kareena as the independent-minded medical student is winsome; debutant Omi has a refreshing flair for comedy and Boman Irani doesn't ham or go over the top even once.

\section{Rating}
4/5







\end{document}
